---
title: "manager"
author: "Kiegan Rice, Heike Hofmann"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
<!-- badges: end -->

The goal of manager is to provide users with tools to use an adaptive computational reproducibility in their data projects. Adaptive computational reproducibility uses a two-step approach:   

1. Define and refine the extent of package dependencies used in a script or project.  
2. Compare package inventories across machines, users, and time to identify changes in functions and objects.  

This is accomplished using package *inventories*.  

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("kiegan/manager")
```
## Take Package Inventory  

We can first take a package inventory for a given set of packages, and visualize the dependency tree implicit when calling that set of packages.  

```{r example, eval = F}
library(manager)
project_inventory <- take_inventory(packages = c("tidyr", "stringr", 
                                                 "purrr", "dplyr", 
                                                 "randomForest")) 
plot_inventory(project_inventory)
```


```{r, echo = F, message = F, warning = F}
library(dplyr)
library(manager)
project_inventory <- readRDS("README_files/data/kiegan_inventory.rda")
plot_inventory(project_inventory)
```

The set of packages at the top of the graphic represent "explicit" package dependencies, which are the packages we want to keep track of. All subsequent layers are "implicit" package dependencies, which arise from calling the set of explicit dependencies.  

We can also store these inventories: 

```{r, eval = F}
store_inventory(project_inventory, filepath = "path/to/storage/folder/inventory.rda")
```

Taking and storing an inventory allows for:  

- Comparison with updated inventories at a later date  
- Sending to team members/collaborators to compare differences across users and machines  

## Compare Package Inventories  

Suppose a colleague sends me their inventory of the same set of packages so we can identify differences. I can load that as "userB_inventory" using the `readRDS()` function and compare the two: 

```{r, echo = F, warning = F, message = F}
userB_inventory <- readRDS("README_files/data/amy_inventory.rda")
```

```{r, eval = F}
ab_compare <- compare_inventory(inventory1 = project_inventory,
                                   inventory2 = userB_inventory,
                                   summary_file = "data/ab_compare.txt")
```

```{r, echo = F}
ab_compare <- compare_inventory(inventory1 = project_inventory,
                                   inventory2 = userB_inventory,
                                   summary_file = "README_files/data/ab_compare.txt")
```

We can then investigate identified differences between the two inventories using the object `ab_compare` and the summary text file generated at the `summary_file` filepath. The summary is printed in the console if no filepath is provided.  


The `$table` element provides a summary table of changed objects and descriptive characteristics of the differences between objects. There is one row for every object which differs between the two inventories.  
```{r}
head(ab_compare$table)
```


The `$objects` element contains the same information as `$table`, but additionally provides more detail, including the deparsed objects for each of the provided inventories for direct comparison. The deparsed objects are found in the  `function_text_inv1` and `function_text_inv2` columns. 
```{r}
head(ab_compare$objects)
```

We can now compare the deparsed text of the function across two inventories:  
```{r}
ab_compare$objects %>% 
  filter(package_name == "dplyr", object_name == "contains") %>% 
  pull(function_text_inv1)
ab_compare$objects %>% 
  filter(package_name == "dplyr", object_name == "contains") %>% 
  pull(function_text_inv2)

```

## Search a Script for Objects Which Differ  

```{r, eval = F}
script_check(compare_object = ab_compare, 
             script_filepath = "path/to/R/script.R") # for an .R script 
script_check(compare_object = ab_compare, 
             script_filepath = "path/to/R/script.Rmd", 
             is_R_script = F) # function will convert .Rmd, .Rnw to .R before parsing  
```
